Diffantom: whole-brain diffusion MRI phantoms derived from real datasets of the \acrlong{hcp}

### 2015-10-01 paper/main.tex
insert Dryad infos

\documentclass[english]{frontiers/frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
\usepackage[mode=buildnew]{standalone}

\usepackage{tikz}
%\setcitestyle{square}
\usepackage{url,lineno,microtype}
\usepackage[toc,nomain,acronym,shortcuts,translate=false]{glossaries}
\usepackage[colorlinks=true,linkcolor=black, citecolor=black!80, urlcolor=black!80]{hyperref}
\usepackage{doi}
\usepackage[onehalfspacing]{setspace}

@@

@@

\section*{Data Sharing}
The first \emph{Diffantom} and its distorted version are available under the \gls*{cc0} using the Dryad Digital Repository
  {\color{red} (reference here when published)}.
The package is organized following the \gls*{bids} standard.
The associated software to ``\emph{diffantomize}'' real \gls*{dmri} datasets is available at \url{https://github.com/oesteban/diffantom}
  under an MIT license.
\emph{Phantomas} is available in \url{https://github.com/ecaruyer/Phantomas} under the revised-BSD license.

>>>>

\documentclass[english]{frontiers/frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
\usepackage[mode=buildnew]{standalone}
\usepackage{tikz}
\usepackage[framemethod=TikZ]{mdframed}
%\setcitestyle{square}
\usepackage{url,lineno,microtype}
\usepackage[toc,nomain,acronym,shortcuts,translate=false]{glossaries}
\usepackage[colorlinks=true,linkcolor=black, citecolor=black!80, urlcolor=black!80]{hyperref}
\usepackage{doi}
\usepackage[onehalfspacing]{setspace}

@@

\begin{mdframed}[hidealllines=true, backgroundcolor=black!60, roundcorner=10pt]
{\color{white} Data associated to this Report is available in the Dryad Digital Repository (\doi{10.5061/dryad.4p080}).}
\end{mdframed}

@@

\section*{Data Sharing}
The first \emph{Diffantom} and its distorted version are available under the \gls*{cc0} using the Dryad Digital Repository
  (\doi{10.5061/dryad.4p080}).
The package is organized following the \gls*{bids} standard.
The associated software to ``\emph{diffantomize}'' real \gls*{dmri} datasets is available at
  \url{https://github.com/oesteban/diffantom} under an MIT license.
\emph{Phantomas} is available in \url{https://github.com/ecaruyer/Phantomas} under the revised-BSD license.
